Behavior Driven Development in Haskell

### 2012-06-01 paper.tex
brush up Conclusion.

This paper discussed how to apply behavior driven development to
Haskell.  We proposed to use Doctest for user documentation and Hspec
for code documentation.  For user documentation, two markups for
properties and examples are added to Haddock.  And we implemented
Doctest to verify examples and test properties from Haddock comments.
For code documentation, a set of combinators for expectations is
extended for Hspec.  With these two tools, specification can also be
used for documentation and automatic testing.  We also described a
mechanism that can automatically discover all specs of a project.  We
think that our approach enhances the value of test code, and we hope
that three-in-one aspect will motivate Haskell programmers to write
more and better

>>>>

This paper discussed how to apply behavior driven development to
Haskell.  We proposed to use Doctest for user documentation and Hspec
for code documentation. We added two markups for
properties and examples to Haddock and implemented
Doctest to verify examples and test properties from Haddock comments.
We also extended a set of combinators for expectations for Hspec.
With these two tools, specification can also be
used for documentation and automatic testing.  We also described a
mechanis that can automatically discover all specs of a project.  We
think that our approach enhances the value of test code, and hope
that three-in-one aspect will motivate Haskell programmers to write
more and better test code.
